Advances in Artificial Intelligence for Data Visualization: Developing Computer Vision Models to Automate Reading of Data Plots, with Application to Predictive Model Diagnostics

### 2022-03-08 Milestone_1/01-chap1.Rmd
finish intro and timeline

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, cache=TRUE)
# Load any R packages you need here
library(ggplot2)
```

@@

@@

## Predictive Modelling and Visual Diagnostics

@@

## Visual Inference

@@

## Pre-specification of Visual Discoverable Features

As discussed in @buja_statistical_2009, in the practice of model diagnostics, the range of possible visual discoveries is not pre-specified. In other words, people do not explicitly specify which visual feature(s) they are looking for before the reading the diagnostic plot. In contrary, conventional hypothesis testing always requires the pre-specification of the parameter space $\Theta$ of the parameter of interest $\theta \in \Theta$ to form a valid inferential procedure. To address this issue, a collection of test statistics $T^{(i)}(\boldsymbol{\mathrm{y}})~(i \in I)$ is defined, where $\boldsymbol{\mathrm{y}}$ is the data and $I$ is a set of all possible visual features. @buja_statistical_2009 described each of the test statistics $T^{(i)}(\boldsymbol{\mathrm{y}})$ as a measurement of the degree of presence of a visual feature. Alternatively, @majumder_validation_2013 avoids the use of visual features and defined the visual statistics $T(.)$ as a mapping from a dataset to a data plot. Both definitions of visual test statistics are valid, but in the rest of the paper the first definition will be used as it covers some details needed by the following discussion.

@@

## Sampling from the Null Distribution

@@

The conditional distribution given a minimal sufficient statistic is the best justified reference distribution among the three [@buja_statistical_2009]. Focus will be put on simulation based on this distribution as it is applicable to classical normal linear regression model. Details of the other two are can be found in the supplementary material of @buja_statistical_2009. Suppose there exists a minimal sufficient statistic $\boldsymbol{S}(\boldsymbol{y})$ under the null hypothesis, any null datasets $\boldsymbol{y^{*}}$ should fulfil the condition $\boldsymbol{S}(\boldsymbol{y}) = \boldsymbol{s}$. For classical normal linear regression model, the minimal sufficient statistic is $\boldsymbol{S}(\boldsymbol{y}) = (\hat{\boldsymbol{\beta}}, \boldsymbol{e}'\boldsymbol{e})$, where $\hat{\boldsymbol{\beta}}$ are the coefficient estimators and $\boldsymbol{e}'\boldsymbol{e}$ is the residual sum of square. Alternatively, the minimal sufficient statistic can be constructed as $\boldsymbol{S}(\boldsymbol{y}) = (\hat{\boldsymbol{y}}, ||\boldsymbol{e}||)$, where $\hat{\boldsymbol{y}}$ are the fitted values and $||\boldsymbol{e}||$ is the length of residuals, which is more intuitive as suggested by @buja_statistical_2009. Since the fitted values are held fixed, the variation can only occur in the residual space. And because the length of residual is also held fixed, residuals obtained from a null dataset has to be a random rotation of $\boldsymbol{e}$ in the residual space. With this property, null residuals can be simulated by regressing $N$ i.i.d standard normal random draws on the regressors, then rescaling it by the ratio of residual sum of square in two regressions.

## Lineup Protocol

@@

## Limitations of Lineup Protocol and Automatic Visual Inference

@@

The "steam engine" of visual inference needs to developed for relieving people's workload by automating repeating tasks and providing standard result in a control environment. Large-scale evaluation of visual tests is not possible without the use of technology and machines.

@@

@@

```{r}
null_true_eval_dat %>%
  group_by(model, null) %>%
  summarise(rate = mean(prediction == null)) %>%
  pivot_wider(names_from = "null", values_from = "rate") %>%
  ungroup() %>%
  mutate(model = model_name) %>%
  mutate(avg_rate = (`FALSE` + `TRUE`)/2) %>%
  knitr::kable(col.names = c("Model", "Actual data plot correct rate", "Null plot correct rate", "Average correct rate"), 
             booktabs = TRUE, 
             caption  = 'Performance of computer vision models on null residual plot and acutal data plot.', 
             label = "null-true-eval" ) 
```

@@

```{r}
cache_env <- new.env()
lineup_eval_summary %>%
  calc_p_value_multi(lineup_id = "set", detected = "detect", n_sel = "n_sel", cache_env = cache_env) -> cv_results
```
```{r}
cv_results %>%
  mutate(reject = eval_p_value(p_value, tol = 1e-2)) %>%
  left_join(select(eval_original_data, id, effect_size) %>%
              group_by(id) %>%
              summarise(effect_size = first(effect_size)),
            by = c("lineup_id" = "id")) -> cv_results

@@

# Timeline (need discussion)

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, cache=TRUE, warning = FALSE)
# Load any R packages you need here
library(tidyverse)
library(visage)
```

@@

The introduction of the report is organised as follows. Section \ref{se:predictive-modelling} discusses the predictive modelling culture and the use of data plots in predictive model diagnostics. Section \ref{se:vi} outlines the definition and terminology of visual inference. Section \ref{se:prespecification} presents the justification of the validity of visual inference. Section \ref{se:sampling-from-null} describes the sampling techniques in visual inference with an example of the classical normal linear regression model. Section \ref{se:lineup} introduces the lineup protocol and the estimation of $p$-value and power of a visual test. And lastly, Section \ref{se:limitation} points out the limitation of lineup protocol, which is also the motivation of this research, and the need of building an automatic visual inference system.

@@

## Predictive Modelling and Visual Diagnostics {#se:predictive-modelling}

@@

## Visual Inference {#se:vi}

@@

## Pre-specification of Visual Discoverable Features {#se:prespecification}

As discussed in @buja_statistical_2009, in the practice of model diagnostics, the range of possible visual discoveries is not pre-specified. In other words, people do not explicitly specify which visual feature(s) they are looking for before the reading the diagnostic plot. In contrary, conventional hypothesis testing always requires the pre-specification of the parameter space $\Theta$ of the parameter of interest $\theta \in \Theta$ to form a valid inferential procedure. To address this issue, a collection of test statistics $T^{(i)}(\boldsymbol{\mathrm{y}})~(i \in I)$ is defined, where $\boldsymbol{\mathrm{y}}$ is the data and $I$ is a set of all possible visual features. @buja_statistical_2009 described each of the test statistics $T^{(i)}(\boldsymbol{\mathrm{y}})$ as a measurement of the degree of presence of a visual feature. Alternatively, @majumder_validation_2013 avoids the use of visual features and defined the visual statistics $T(.)$ as a mapping from a dataset to a data plot. Both definitions of visual test statistics are valid, but in the rest of the report the first definition will be used as it covers some details needed by the following discussion.

@@

## Sampling from the Null Distribution {#se:sampling-from-null}

@@

The conditional distribution given a minimal sufficient statistic is the best justified reference distribution among the three [@buja_statistical_2009]. Suppose there exists a minimal sufficient statistic $\boldsymbol{S}(\boldsymbol{y})$ under the null hypothesis, any null datasets $\boldsymbol{y^{*}}$ should fulfil the condition $\boldsymbol{S}(\boldsymbol{y}) = \boldsymbol{s}$. Using the classical linear regression model as example, the minimal sufficient statistic is $\boldsymbol{S}(\boldsymbol{y}) = (\hat{\boldsymbol{\beta}}, \boldsymbol{e}'\boldsymbol{e})$, where $\hat{\boldsymbol{\beta}}$ are the coefficient estimators and $\boldsymbol{e}'\boldsymbol{e}$ is the residual sum of square. Alternatively, the minimal sufficient statistic can be constructed as $\boldsymbol{S}(\boldsymbol{y}) = (\hat{\boldsymbol{y}}, ||\boldsymbol{e}||)$, where $\hat{\boldsymbol{y}}$ are the fitted values and $||\boldsymbol{e}||$ is the length of residuals, which is more intuitive as suggested by @buja_statistical_2009. Since the fitted values are held fixed, the variation can only occur in the residual space. And because the length of residual is also held fixed, residuals obtained from a null dataset has to be a random rotation of $\boldsymbol{e}$ in the residual space. With this property, null residuals can be simulated by regressing $N$ i.i.d standard normal random draws on the regressors, then rescaling it by the ratio of residual sum of square in two regressions.

## Lineup Protocol {#se:lineup}

@@

## Limitations of Lineup Protocol and Automatic Visual Inference {#se:limitation}

@@

The "steam engine" of visual inference needs to be developed for relieving people's workload by automating repeating tasks and providing standard result in a control environment. Large-scale evaluation of visual tests is not possible without the use of technology and machines.

@@

The

The first project is

@@

```{r}
null_true_eval_dat %>%
  mutate(type = ifelse(id <= 5000, "Cubic", "Heteroskedasticity")) %>% 
  group_by(model, type, null) %>%
  summarise(rate = mean(prediction == null)) %>%
  pivot_wider(names_from = "null", values_from = "rate") %>%
  ungroup() %>%
  mutate(avg_rate = (`FALSE` + `TRUE`)/2) %>%
  select(-model) %>%
  knitr::kable(col.names = c("", "Actual data plot detection rate", "Null plot detection rate", "Average detection rate"), 
             booktabs = TRUE, 
             caption  = 'Performance of computer vision models on null residual plot and acutal data plot.', 
             label = "null-true-eval" ) %>%
  kableExtra::kable_styling(latex_options = "scale_down") %>%
  kableExtra::pack_rows("VGG16", 1, 2, bold = TRUE, italic = TRUE, underline = TRUE) %>%
  kableExtra::pack_rows("VGG19", 3, 4, bold = TRUE, italic = TRUE, underline = TRUE) %>%
  kableExtra::pack_rows("Xception", 5, 6, bold = TRUE, italic = TRUE, underline = TRUE) %>%
  kableExtra::pack_rows("ResNet152V2", 7, 8, bold = TRUE, italic = TRUE, underline = TRUE) %>%
  kableExtra::pack_rows("InceptionV3", 9, 10, bold = TRUE, italic = TRUE, underline = TRUE)
```

@@

```{r}
cache_env <- new.env()
lineup_eval_summary %>%
  calc_p_value_multi(lineup_id = "set", detected = "detect", n_sel = "n_sel", cache_env = cache_env) -> cv_results
```

```{r}
cv_results %>%
  mutate(reject = eval_p_value(p_value, tol = 1e-2)) %>%
  left_join(select(eval_original_data, id, effect_size) %>%
              group_by(id) %>%
              summarise(effect_size = first(effect_size)),
            by = c("lineup_id" = "id")) -> cv_results

@@

```{r}
lineup_eval_dat %>%
  left_join(eval_lineup_ans, by = c("set" = "id", "plot" = "k")) %>%
  filter(ans == TRUE) %>%
  group_by(set, model) %>%
  summarise(pseudo_predict = sample(predict, 1)) -> pseudo_predict_dat

lineup_eval_dat %>%
  left_join(eval_lineup_ans, by = c("set" = "id", "plot" = "k")) %>%
  left_join(pseudo_predict_dat) %>%
  mutate(predict = ifelse(ans == FALSE, pseudo_predict, predict)) %>%
  group_by(model, set) %>%
  summarise(n_sel = sum(!predict), detect = sum(ans == FALSE & predict == FALSE))  -> lineup_pseudo_summary

lineup_pseudo_summary %>%
  calc_p_value_multi(lineup_id = "set", detected = "detect", n_sel = "n_sel", cache_env = cache_env) -> pseudo_results

pseudo_results %>%
  mutate(reject = eval_p_value(p_value, tol = 1e-2)) %>%
  mutate(type = ifelse(lineup_id <= 2500, "Cubic", "Heteroskedasticity")) %>%
  group_by(type) %>%
  summarise(rate = mean(reject))
```

# Timeline

\begin{table} \label{tab:timeline}
\centering
\begin{tabular}[t]{ll}
\toprule
\addlinespace[0.5em]
Date & Event\\
\addlinespace[0.5em]
\midrule
\addlinespace[0.5em]
\multicolumn{2}{l}{\textit{\textbf{2022}}}\\
\hspace{4em}March & Extend the scope of violations of classical normal linear\\ 
\addlinespace[0.5em]
\hspace{4em} & regression considered by the computer vision model\\
\addlinespace[0.5em]
\hspace{4em}April & Conduct human subject experiment on the extended model\\ 
\addlinespace[0.5em]
\hspace{4em} & defects\\
\addlinespace[0.5em]
\hspace{4em}May & Conclude the first project: draft and submit the first paper\\
\addlinespace[0.5em]
\hspace{4em}June & Review previous studies in image comparison\\
\addlinespace[0.5em]
\hspace{4em}July & Propose a new design of the automatic visual inference\\
\addlinespace[0.5em]
\hspace{4em} & system based on image comparison\\
\addlinespace[0.5em]
\hspace{4em}August - November & Develop the proposed system\\
\addlinespace[0.5em]
\hspace{4em}November - December & Conduct human subject experiment for validating the\\
\addlinespace[0.5em]
\hspace{4em} & proposed system\\
\addlinespace[0.5em]
\hspace{4em}December & Attend the Australasian Applied Statistics Conference\\
\addlinespace[0.5em]
\hline
\addlinespace[0.5em]
\multicolumn{2}{l}{\textit{\textbf{2023}}}\\
\hspace{4em}January - March & Finish the second project: prepare milestone material and\\
\addlinespace[0.5em]
\hspace{4em} & submit the second paper\\
\addlinespace[0.5em]
\hspace{4em}April - December & Apply the automatic visual inference system to predictive\\
\addlinespace[0.5em]
\hspace{4em} & model diagnostics\\
\addlinespace[0.5em]
\hline
\addlinespace[0.5em]
\multicolumn{2}{l}{\textit{\textbf{2024}}}\\
\hspace{4em}January - March & Finish the third project: finalize the thesis\\
\addlinespace[0.5em]
\bottomrule
\end{tabular}
\end{table}

### 2022-03-08 Milestone_1/_book/thesis.tex
finish intro and timeline

\hypertarget{predictive-modelling-and-visual-diagnostics}{%
\section{Predictive Modelling and Visual Diagnostics}\label{predictive-modelling-and-visual-diagnostics}}

@@

\hypertarget{visual-inference}{%
\section{Visual Inference}\label{visual-inference}}

@@

\hypertarget{pre-specification-of-visual-discoverable-features}{%
\section{Pre-specification of Visual Discoverable Features}\label{pre-specification-of-visual-discoverable-features}}

As discussed in \textcite{buja_statistical_2009}, in the practice of model diagnostics, the range of possible visual discoveries is not pre-specified. In other words, people do not explicitly specify which visual feature(s) they are looking for before the reading the diagnostic plot. In contrary, conventional hypothesis testing always requires the pre-specification of the parameter space \(\Theta\) of the parameter of interest \(\theta \in \Theta\) to form a valid inferential procedure. To address this issue, a collection of test statistics \(T^{(i)}(\boldsymbol{\mathrm{y}})~(i \in I)\) is defined, where \(\boldsymbol{\mathrm{y}}\) is the data and \(I\) is a set of all possible visual features. \textcite{buja_statistical_2009} described each of the test statistics \(T^{(i)}(\boldsymbol{\mathrm{y}})\) as a measurement of the degree of presence of a visual feature. Alternatively, \textcite{majumder_validation_2013} avoids the use of visual features and defined the visual statistics \(T(.)\) as a mapping from a dataset to a data plot. Both definitions of visual test statistics are valid, but in the rest of the paper the first definition will be used as it covers some details needed by the following discussion.

@@

\hypertarget{sampling-from-the-null-distribution}{%
\section{Sampling from the Null Distribution}\label{sampling-from-the-null-distribution}}

@@

The conditional distribution given a minimal sufficient statistic is the best justified reference distribution among the three \autocite{buja_statistical_2009}. Focus will be put on simulation based on this distribution as it is applicable to classical normal linear regression model. Details of the other two are can be found in the supplementary material of \textcite{buja_statistical_2009}. Suppose there exists a minimal sufficient statistic \(\boldsymbol{S}(\boldsymbol{y})\) under the null hypothesis, any null datasets \(\boldsymbol{y^{*}}\) should fulfil the condition \(\boldsymbol{S}(\boldsymbol{y}) = \boldsymbol{s}\). For classical normal linear regression model, the minimal sufficient statistic is \(\boldsymbol{S}(\boldsymbol{y}) = (\hat{\boldsymbol{\beta}}, \boldsymbol{e}'\boldsymbol{e})\), where \(\hat{\boldsymbol{\beta}}\) are the coefficient estimators and \(\boldsymbol{e}'\boldsymbol{e}\) is the residual sum of square. Alternatively, the minimal sufficient statistic can be constructed as \(\boldsymbol{S}(\boldsymbol{y}) = (\hat{\boldsymbol{y}}, ||\boldsymbol{e}||)\), where \(\hat{\boldsymbol{y}}\) are the fitted values and \(||\boldsymbol{e}||\) is the length of residuals, which is more intuitive as suggested by \textcite{buja_statistical_2009}. Since the fitted values are held fixed, the variation can only occur in the residual space. And because the length of residual is also held fixed, residuals obtained from a null dataset has to be a random rotation of \(\boldsymbol{e}\) in the residual space. With this property, null residuals can be simulated by regressing \(N\) i.i.d standard normal random draws on the regressors, then rescaling it by the ratio of residual sum of square in two regressions.

\hypertarget{lineup-protocol}{%
\section{Lineup Protocol}\label{lineup-protocol}}

@@

\hypertarget{limitations-of-lineup-protocol-and-automatic-visual-inference}{%
\section{Limitations of Lineup Protocol and Automatic Visual Inference}\label{limitations-of-lineup-protocol-and-automatic-visual-inference}}

@@

The ``steam engine'' of visual inference needs to developed for relieving people's workload by automating repeating tasks and providing standard result in a control environment. Large-scale evaluation of visual tests is not possible without the use of technology and machines.

@@

\begin{verbatim}
##          y          x    sigma         e     .resid  .fitted
## 1 7.205499  0.9053470 5.218132 5.3001525  0.7420902 6.463409
## 2 2.560696 -0.8626811 4.981465 2.4233771  1.0441078 1.516588
## 3 1.121106 -0.6545505 3.835357 0.7756568 -0.9778170 2.098923
## 4 5.296467  0.7171334 4.178154 3.5793335 -0.6403337 5.936801
## 5 2.962130 -0.2859733 1.901837 2.2481030 -0.1680473 3.130177
\end{verbatim}

@@

\begin{verbatim}
##       0       1       2       3 
## 0.70182 0.25202 0.04346 0.00270
\end{verbatim}

@@

\begin{verbatim}
## [1] 0.04688
\end{verbatim}

@@

\caption{\label{tab:null-true-eval}Performance of computer vision models on null residual plot and acutal data plot.}
\centering
\begin{tabular}[t]{lrrr}
\toprule
Model & Actual data plot correct rate & Null plot correct rate & Average correct rate\\
\midrule
VGG16 & 0.7387 & 0.8850 & 0.81185\\
VGG19 & 0.8029 & 0.8313 & 0.81710\\
Xception & 0.7370 & 0.9213 & 0.82915\\
ResNet152V2 & 0.6932 & 0.9233 & 0.80825\\
InceptionV3 & 0.6691 & 0.9399 & 0.80450\\
\bottomrule
\end{tabular}
\end{table}

@@

\hypertarget{timeline-need-discussion}{%
\chapter{Timeline (need discussion)}\label{timeline-need-discussion}}

>>>>

The introduction of the report is organised as follows. Section \ref{se:predictive-modelling} discusses the predictive modelling culture and the use of data plots in predictive model diagnostics. Section \ref{se:vi} outlines the definition and terminology of visual inference. Section \ref{se:prespecification} presents the justification of the validity of visual inference. Section \ref{se:sampling-from-null} describes the sampling techniques in visual inference with an example of the classical normal linear regression model. Section \ref{se:lineup} introduces the lineup protocol and the estimation of \(p\)-value and power of a visual test. And lastly, Section \ref{se:limitation} points out the limitation of lineup protocol, which is also the motivation of this research, and the need of building an automatic visual inference system.

\hypertarget{se:predictive-modelling}{%
\section{Predictive Modelling and Visual Diagnostics}\label{se:predictive-modelling}}

@@

\hypertarget{se:vi}{%
\section{Visual Inference}\label{se:vi}}

@@

\hypertarget{se:prespecification}{%
\section{Pre-specification of Visual Discoverable Features}\label{se:prespecification}}

As discussed in \textcite{buja_statistical_2009}, in the practice of model diagnostics, the range of possible visual discoveries is not pre-specified. In other words, people do not explicitly specify which visual feature(s) they are looking for before the reading the diagnostic plot. In contrary, conventional hypothesis testing always requires the pre-specification of the parameter space \(\Theta\) of the parameter of interest \(\theta \in \Theta\) to form a valid inferential procedure. To address this issue, a collection of test statistics \(T^{(i)}(\boldsymbol{\mathrm{y}})~(i \in I)\) is defined, where \(\boldsymbol{\mathrm{y}}\) is the data and \(I\) is a set of all possible visual features. \textcite{buja_statistical_2009} described each of the test statistics \(T^{(i)}(\boldsymbol{\mathrm{y}})\) as a measurement of the degree of presence of a visual feature. Alternatively, \textcite{majumder_validation_2013} avoids the use of visual features and defined the visual statistics \(T(.)\) as a mapping from a dataset to a data plot. Both definitions of visual test statistics are valid, but in the rest of the report the first definition will be used as it covers some details needed by the following discussion.

@@

\hypertarget{se:sampling-from-null}{%
\section{Sampling from the Null Distribution}\label{se:sampling-from-null}}

@@

The conditional distribution given a minimal sufficient statistic is the best justified reference distribution among the three \autocite{buja_statistical_2009}. Suppose there exists a minimal sufficient statistic \(\boldsymbol{S}(\boldsymbol{y})\) under the null hypothesis, any null datasets \(\boldsymbol{y^{*}}\) should fulfil the condition \(\boldsymbol{S}(\boldsymbol{y}) = \boldsymbol{s}\). Using the classical linear regression model as example, the minimal sufficient statistic is \(\boldsymbol{S}(\boldsymbol{y}) = (\hat{\boldsymbol{\beta}}, \boldsymbol{e}'\boldsymbol{e})\), where \(\hat{\boldsymbol{\beta}}\) are the coefficient estimators and \(\boldsymbol{e}'\boldsymbol{e}\) is the residual sum of square. Alternatively, the minimal sufficient statistic can be constructed as \(\boldsymbol{S}(\boldsymbol{y}) = (\hat{\boldsymbol{y}}, ||\boldsymbol{e}||)\), where \(\hat{\boldsymbol{y}}\) are the fitted values and \(||\boldsymbol{e}||\) is the length of residuals, which is more intuitive as suggested by \textcite{buja_statistical_2009}. Since the fitted values are held fixed, the variation can only occur in the residual space. And because the length of residual is also held fixed, residuals obtained from a null dataset has to be a random rotation of \(\boldsymbol{e}\) in the residual space. With this property, null residuals can be simulated by regressing \(N\) i.i.d standard normal random draws on the regressors, then rescaling it by the ratio of residual sum of square in two regressions.

\hypertarget{se:lineup}{%
\section{Lineup Protocol}\label{se:lineup}}

@@

\hypertarget{se:limitation}{%
\section{Limitations of Lineup Protocol and Automatic Visual Inference}\label{se:limitation}}

@@

The ``steam engine'' of visual inference needs to be developed for relieving people's workload by automating repeating tasks and providing standard result in a control environment. Large-scale evaluation of visual tests is not possible without the use of technology and machines.

@@

\begin{verbatim}
##            y          x    sigma          e     .resid    .fitted
## 1 -7.6931740  0.8335218 4.819987 -9.5266958 -5.7469121 -1.9462619
## 2  7.0213194 -0.7458772 4.336202  6.7671966 -0.9130225  7.9343418
## 3 -2.1856528  0.9509873 5.471751 -4.1366401  0.4954643 -2.6811172
## 4  4.0402811  0.4961018 2.979219  2.5441792  3.8756685  0.1646126
## 5  0.8686919  0.7494172 4.355690 -0.8807253  2.2888017 -1.4201098
\end{verbatim}

@@

\begin{verbatim}
##       0       1       2       3 
## 0.70094 0.25280 0.04340 0.00286
\end{verbatim}

@@

\begin{verbatim}
## [1] 0.0456
\end{verbatim}

@@

\caption{\label{tab:null-true-eval}Performance of computer vision models on null residual plot and acutal data plot.}
\centering
\resizebox{\linewidth}{!}{
\begin{tabular}[t]{lrrr}
\toprule
 & Actual data plot detection rate & Null plot detection rate & Average detection rate\\
\midrule
\addlinespace[0.3em]
\multicolumn{4}{l}{\underline{\textit{\textbf{VGG16}}}}\\
\hspace{1em}Cubic & 0.7752 & 0.8662 & 0.8207\\
\hspace{1em}Heteroskedasticity & 0.7022 & 0.9038 & 0.8030\\
\addlinespace[0.3em]
\multicolumn{4}{l}{\underline{\textit{\textbf{VGG19}}}}\\
\hspace{1em}Cubic & 0.8006 & 0.8210 & 0.8108\\
\hspace{1em}Heteroskedasticity & 0.8052 & 0.8416 & 0.8234\\
\addlinespace[0.3em]
\multicolumn{4}{l}{\underline{\textit{\textbf{Xception}}}}\\
\hspace{1em}Cubic & 0.7442 & 0.9182 & 0.8312\\
\hspace{1em}Heteroskedasticity & 0.7298 & 0.9244 & 0.8271\\
\addlinespace[0.3em]
\multicolumn{4}{l}{\underline{\textit{\textbf{ResNet152V2}}}}\\
\hspace{1em}Cubic & 0.7252 & 0.9168 & 0.8210\\
\hspace{1em}Heteroskedasticity & 0.6612 & 0.9298 & 0.7955\\
\addlinespace[0.3em]
\multicolumn{4}{l}{\underline{\textit{\textbf{InceptionV3}}}}\\
\hspace{1em}Cubic & 0.6984 & 0.9304 & 0.8144\\
\hspace{1em}Heteroskedasticity & 0.6398 & 0.9494 & 0.7946\\
\bottomrule
\end{tabular}}
\end{table}

@@

\begin{verbatim}
## # A tibble: 2 x 2
##   type                 rate
##   <chr>               <dbl>
## 1 Cubic              0.0056
## 2 Heteroskedasticity 0.006
\end{verbatim}

\hypertarget{timeline}{%
\chapter{Timeline}\label{timeline}}

\begin{table} \label{tab:timeline}
\centering
\begin{tabular}[t]{ll}
\toprule
\addlinespace[0.5em]
Date & Event\\
\addlinespace[0.5em]
\midrule
\addlinespace[0.5em]
\multicolumn{2}{l}{\textit{\textbf{2022}}}\\
\hspace{4em}March & Extend the scope of violations of classical normal linear\\ 
\addlinespace[0.5em]
\hspace{4em} & regression considered by the computer vision model\\
\addlinespace[0.5em]
\hspace{4em}April & Conduct human subject experiment on the extended model\\ 
\addlinespace[0.5em]
\hspace{4em} & defects\\
\addlinespace[0.5em]
\hspace{4em}May & Conclude the first project: draft and submit the first paper\\
\addlinespace[0.5em]
\hspace{4em}June & Review previous studies in image comparison\\
\addlinespace[0.5em]
\hspace{4em}July & Propose a new design of the automatic visual inference\\
\addlinespace[0.5em]
\hspace{4em} & system based on image comparison\\
\addlinespace[0.5em]
\hspace{4em}August - November & Develop the proposed system\\
\addlinespace[0.5em]
\hspace{4em}November - December & Conduct human subject experiment for validating the\\
\addlinespace[0.5em]
\hspace{4em} & proposed system\\
\addlinespace[0.5em]
\hspace{4em}December & Attend the Australasian Applied Statistics Conference\\
\addlinespace[0.5em]
\hline
\addlinespace[0.5em]
\multicolumn{2}{l}{\textit{\textbf{2023}}}\\
\hspace{4em}January - March & Finish the second project: prepare milestone material and\\
\addlinespace[0.5em]
\hspace{4em} & submit the second paper\\
\addlinespace[0.5em]
\hspace{4em}April - December & Apply the automatic visual inference system to predictive\\
\addlinespace[0.5em]
\hspace{4em} & model diagnostics\\
\addlinespace[0.5em]
\hline
\addlinespace[0.5em]
\multicolumn{2}{l}{\textit{\textbf{2024}}}\\
\hspace{4em}January - March & Finish the third project: finalize the thesis\\
\addlinespace[0.5em]
\bottomrule
\end{tabular}
\end{table}
